Algebraic File Synchronization: Adequacy and Completeness

### 2017-10-19 p2/def-commands.tex
Completed the completeness theorem

\begin{mydef}[Effect of commands]
We use a replacement operator of the form
$\FS_{[\valv/n]}$ to denote a filesystem derived from $\FS$ 
by replacing its value at $n$ with $\valv$:
\[ \FS_{[\valv/n]}(m) =
   \begin{cases}
   \valv &\mbox{if~} m=n\\
   \FS(m) &\mbox{otherwise.}
   \end{cases}
\]
The effect of the commands is then as follows:
\begin{align*}
&\cbrk\aFS = \fsbroken \\
&\cxynv\aFS = 
   \begin{cases}
   % \fsbroken &\mbox{if~} \FS=\fsbroken\\
   \fsbroken &\mbox{if~} [\FS(n)]\neq[x]\\
   \fsbroken &\mbox{if~} \FS_{[y/n]} \mbox{~violates the tree property}\\
   \FS_{[y/n]} &\mbox{otherwise.}
   \end{cases}
\end{align*}
\end{mydef}

>>>>

\begin{mydef}[Effect of commands]
We use a replacement operator of the form
$\fsreplacement{\FS}{n}{\valv}$ to denote a filesystem derived from $\FS$ 
by replacing its value at $n$ with $\valv$:
\[ \fsreplacement{\FS}{n}{\valv}(m) =
   \begin{cases}
   \valv &\mbox{if~} m=n\\
   \FS(m) &\mbox{otherwise.}
   \end{cases}
\]
The effect of the commands is then as follows:
\begin{align*}
&\cbrk\aFS = \fsbroken \\
&\cxynv\aFS = 
   \begin{cases}
   % \fsbroken &\mbox{if~} \FS=\fsbroken\\
   \fsbroken &\mbox{if~} [\FS(n)]\neq[x]\\
   \fsbroken &\mbox{if~} \fsreplacement{\FS}{n}{y} \mbox{~violates the tree property}\\
   \fsreplacement{\FS}{n}{y} &\mbox{otherwise.}
   \end{cases}
\end{align*}
\end{mydef}

### 2017-10-19 p2/rec-complete.tex
Completed the completeness theorem

First, we prove that this sequence breaks all filesystems
where $A$ and $B$ are defined unless $n=m$.
Let us therefore suppose $n\neq m$ and, to use an inverse proof,
that the sequence is defined on $\FS$ where $A\aFS\neq\fsbroken$.
If so, its initial segment, $\acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv$ must also be defined.

We know $\cxynv\nindep\czwmv$, and so from \cref{incomparable_is_independent}, $n\nunrel m$.
As the sequence is defined on $\FS$, $\czwmv\cc\cxynv$ can only be a construction or destruction pair.
Also, because $B$ is simple and contains $\czwmv$,
we know there are no commands on $m$ 
in either $\acb$ or $T_0$, which are both formed from other commands in $B$.
Moreover, we know there are no commands on $m$ in $S_0$ because $S_0\indep T$.

TODO TODO TODO

On the one hand, we therefore know that $\FS(m)$ must be of type $[z]$,
but on the other, from \cref{ax_directchild_breaks,ax_directparent_breaks},
we also know that $\cxynv$ cannot be applied to $\FS$ without
changing $\FS(m)$ first.
As $A\aFS\neq\fsbroken$, this means that $A$ must contain a command on $m$.
Let this command be $\cqrmv$.

Clearly $[q]=[z]$ (from \cref{worksinputmatch}), and from the construction and destruction
pairs we also see that $r=w$ must hold, where $w=\vald$ or $w=\empt$.
As $|\setd|=1$ and $|\setb|=1$, this also means that $::v_R=v_W::$ and therefore
$\cqrmv = \czwmv$.
This is a contradiction as $\cqrmv\in A$, but $\czwmv\in\bmanp$.

The only possibility is therefore $n=m$.
As $A$ and $B$ are simple, we therefore know that these are the first commands on $n$,
and so (again from \cref{worksinputmatch}) $[z]=[x]$.
We also know $w\neq y$ as otherwise the two commands would be equal and
would be included in $\acbnp$,
but this means that $\cxynv$, from $A$, overrides a change introduced 
by $\czwnv$, from $B$, which should be treated as a conflict.
\end{proof}

>>>>

First, we prove that this sequence breaks all filesystems
where $A$ and $B$ are defined unless $n=m$.
Let us therefore suppose $n\neq m$ and, to use an inverse proof,
that the sequence is defined on $\FS$ 
where $A\aFS\neq\fsbroken$ and $B\aFS\neq\fsbroken$.
If so, its initial segment,
\[ \acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv, \]
must also be defined on $\FS$.

We know $\cxynv\nindep\czwmv$, and so from \cref{incomparable_is_independent}, $n\nunrel m$.
As the sequence is defined on $\FS$,
because of \cref{simple_distant_pairs}
$\czwmv\cc\cxynv$ can only be a construction or destruction pair.

Also, because $B$ is simple and contains $\czwmv$,
we know there are no commands on $m$ 
in either $\acb$ or $T_0$, which are both formed from other commands in $B$.
Moreover, we know there are no commands on $m$ in $S_0$ because $S_0\indep T$.
We therefore know that $\FS(m)$ must be of type $[z]$.

If $m=\parentf{n}$ then $\czwmv\cc\cxynv$ is a construction pair, and we know
$[\FS(m)]=[z]\neq[\vald]$ and $y\neq\empt$ as none of these commands is an assertion command.
If so, $\fsreplacement{\FS}{n}{y}$ 
(that is, applying $\cxynv$ to $\FS$ without modifying $\FS(m)$ first) would violate the tree property.
The same is true when $\parentf{m}=n$, where we have a destruction pair,
and $[z]\neq\empt$ and $[y]\neq[\vald]$.

Since $\cxynv\in S$ and therefore $\cxynv\in A$, and $A\aFS\neq\fsbroken$,
the above means that $A$ must also contain a command on $m$ before $\cxynv$.
From \cref{simple_distant_pairs} we then know that $\cqrmv\cc\cxynv$
is also a construction or destruction pair, and it is the same type as
$\czwmv\cc\cxynv$.

Because the type of the pair determines the output type of the first command,
this means that $[r]=[w]$, and they can either be $[\empt]$ or $[\vald]$.
As we assumed that $|\setd|=1$, we therefore know that $r=w$.
From \cref{worksinputmatch} we also know that $[q]=[z]$.

Therefore $\cqrmv = \czwmv$, which is a contradiction
because $\cqrmv$ was selected from $A$, and
$\czwmv$ was selected from $T$, that is, from $\bmanp$.

The only possibility is therefore $n=m$.
As $A$ and $B$ are simple, we then know that
$\cxynv$ and $\czwmv$ are the first commands on $n$,
and so (again from \cref{worksinputmatch}) $[z]=[x]$.
We also know $w\neq y$ as otherwise the two commands would be equal and
would be in $\acbnp$.
This, however, means that $\cxynv$, from $A$, overrides a change introduced 
by $\czwnv$, from $B$, which must be treated as a conflict.
\end{proof}
